---
title: "Comps Graphics"
author: "Tommy Jones"
date: "4/9/2020"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, cache = TRUE, cache.lazy = FALSE)
```

## Purpose

This pulls together graphics and other outputs. To run this .Rmd file, you must run each of the scripts in the "R/" directory in order from "01_format_data.R" to "04_lda_retrain.R". A warning: these scripts, run all the way through, will take substantial memory and ~3 days runtime (at least on my 2019 Macbook Pro). 

```{r}
library(textmineR)

library(tidylda)

library(tidyverse)

library(cluster)

library(patchwork)
```


## Initial Corpus Summary

```{r}
load("data_derived/20_newsgroups_formatted.RData")


# frequency of top 20 terms
# function to get this by class or overall
top_20 <- function(tf_tibble) {
  
  tf_tibble %>%
    select(term, term_freq) %>%
    arrange(desc(term_freq)) %>%
    top_n(20) 
  
}

# overall 
tf_bigram %>%
  select(term, term_freq) %>%
  arrange(desc(term_freq)) %>%
  top_n(20) %>%
  ggplot() + 
  geom_bar(aes(x = reorder(term, term_freq), y = term_freq), 
           stat = "identity", fill = "#fc8d62") + 
  coord_flip() +
  labs(x = "", y = "Frequency", 
       title = "Most Frequent Terms in 20 Newsgropus, Excluding Stop Words")
  

# distribution of each class
tibble(class = doc_class) %>%
  count(class) %>%
  ggplot() + 
  geom_bar(aes(x = class, y = n), stat = "identity", fill = "#66c2a5") +
  coord_flip() +
  labs(x = "", y = "Frequency", title = "Freqency of Class in 20 Newsgroups Data")

# top 20 for each class
top_20_by_class <- lapply(
  unique(doc_class),
  function(x) {
    out <- top_20(TermDocFreq(dtm_bigram[doc_class == x, ]))
    out$class <- x
    as_tibble(out)
  }
)

for (d in top_20_by_class) {
  plot(
    ggplot(d) +
      geom_bar(aes(x = reorder(term, term_freq), y = term_freq), 
               stat = "identity", fill = "#fc8d62") + 
      coord_flip() +
      labs(x = "", y = "Frequency", 
           title = paste0("Most Frequent Terms in for Class: ", d$class[1]))
  )
}

```



## Clustering

```{r}
rm(list = ls())

load("data_derived/20_newsgroups_formatted.RData")

load("data_derived/cluster_eval.RData")
```

```{r, fig.height = 20, fig.width=30}
# plot the dendrogram
plot(h, labels = rep("", length(h$labels)))
```

```{r fig.height = 9, fig.width = 9}
# plot metrics to choose number of clusters
clust_plot_s <- 
  ggplot(eval_mat) +
  geom_line(aes(x = k, y = avg_silh), color = "#66c2a5", size = 1.3) + 
  labs(x = "Number of Clusters", y = "",
       title = "Silhouette Coefficient")

clust_plot_d <-
  ggplot(eval_mat) +
  geom_line(aes(x = k, y = avg_within_dist), color = "#fc8d62", size = 1.3) + 
  labs(x = "Number of Clusters", y = "",
       title = "Average Intra-Cluster Distances")

clust_plot_c <-
  ggplot(eval_mat) +
  geom_line(aes(x = k, y = coherence), color = "#8da0cb", size = 1.3) + 
  labs(x = "Number of Clusters", y = "",
       title = "Semantic Coherence")

clust_plot_d / clust_plot_s / clust_plot_c

```

```{r}

```

```{r}
# If you want any plots or output from the above calc, put them here...
```

## Choose the number of topics

```{r}
rm(list = ls())

load("data_derived/eval_lda_choose_k.RData")

```


```{r, fig.height = 9, fig.width = 9}

lda_plot_c <- 
  ggplot(eval_lda, aes(x = k, y = coherence_out)) + 
  geom_point(color = "#66c2a5") +
  geom_smooth() + 
  labs(x = "Number of Topics",
       y = "",
       title = "Semantic Coherence")

lda_plot_p <- 
  ggplot(eval_lda, aes(x = k, y = perplexity_out)) + 
  geom_point(color = "#fc8d62") +
  geom_smooth() + 
  labs(x = "Number of Topics",
       y = "",
       title = "Perplexity")

lda_plot_l <- 
  ggplot(eval_lda, aes(x = k, y = likelihood_out)) + 
  geom_point(color = "#8da0cb") +
  geom_smooth() + 
  labs(x = "Number of Topics",
       y = "",
       title = "Log Likelihood")

lda_plot_c / lda_plot_p / lda_plot_l

```


## Convergence exercises

```{r}
rm(list = ls())

load("data_derived/lda_retrain.RData")
```


```{r fig.height = 9, fig.width = 9}

ll1 <- result[[1]]$log_likelihood %>%
  ggplot() + 
  geom_line(aes(x = iteration, y = log_likelihood), color = "#66c2a5", size = 1.3) +
  labs(x = "Iteration",
       y = "",
       title = "1,000 Iterations Straight")

ll2 <- result[[2]]$likelihoods %>%
  ggplot() + 
  geom_line(aes(x = iteration, y = log_likelihood), color = "#fc8d62", size = 1.3) +
  labs(x = "Iteration",
       y = "",
       title = "200 Iterations then 800 Iterations")

ll3 <- result[[3]]$likelihoods %>%
  ggplot() + 
  geom_line(aes(x = iteration, y = log_likelihood), color = "#8da0cb", size = 1.3) +
  labs(x = "Iteration",
       y = "",
       title = "200 Iterations X 5")

ll1 / ll2 / ll3

```


## Analysis of topics and clusters

```{r}

rm(list = ls())

load("data_derived/lda_retrain.RData")

load("data_derived/compare_models.RData")

load("data_derived/model_layouts.RData")

load("data_derived/cluster_summary.RData")

load("data_derived/cluster_solution.RData")

```

```{r}
# layout of topics on their own
topic_summary <- 
  result[[1]]$summary %>%  
  mutate(
    x = topic_layout[, 1], 
    y = topic_layout[, 2]
  )

ggplot(topic_summary) +
  geom_point(
    aes(x = x, y = y, size = prevalence, color = coherence), 
    alpha = 0.65
  ) + 
  labs(
    x = "",
    y = "",
    title = "Intertopic distance map of LDA - 507 topics"
  ) + 
  scale_color_distiller(type = "div", palette = 9) + 
  theme_dark()

# layout of clusters and topics
tc_summary <- 
  cluster_summary %>%
  mutate(
    prevalence = num_tokens / sum(num_tokens) * 100,
    is_cluster = "yes",
    topic = str_c("c_", cluster)
  ) %>%
  select(topic, prevalence, coherence, is_cluster, top_terms)
  
tc_summary <- rbind(
  topic_summary %>% 
    mutate(is_cluster = "no", topic = as.character(topic)) %>%
    select(topic, prevalence, coherence, is_cluster, top_terms),
  tc_summary
) %>%
  mutate(x = cluster_topic_layout[, 1], y = cluster_topic_layout[, 2])

# colored by cluster/topic
ggplot(tc_summary) +
  geom_point(
    aes(x = x, y = y, size = prevalence, color = is_cluster), 
    alpha = 0.65
  ) + 
  labs(
    x = "",
    y = "",
    title = "Intertopic distance map of LDA (507) and Clustering (1,000)"
  ) + 
  scale_color_brewer(type = "qual", palette = 7) + 
  theme_dark()

# colored by coherence
ggplot(tc_summary) +
  geom_point(
    aes(x = x, y = y, size = prevalence, color = coherence), 
    alpha = 0.65
  ) + 
  labs(
    x = "",
    y = "",
    title = "Intertopic distance map of LDA (507) and Clustering (1,000)"
  ) + 
  scale_color_distiller(type = "div", palette = 9) + 
  theme_dark()

# distribution of coherence and log(prevalence)
ggplot(tc_summary) + 
  geom_freqpoly(
    aes(x = log(prevalence), y = ..density.., color = is_cluster)
  ) + 
  labs(title = "Distribution of log(Prevalence)")

ggplot(tc_summary) + 
  geom_freqpoly(
    aes(x = coherence, y = ..density.., color = is_cluster)
  ) + 
  labs(title = "Distribution of Coherence")

# Most prevalent topics and clusters
tc_summary %>%
  arrange(desc(prevalence)) %>%
  select(topic, prevalence, coherence, is_cluster, top_terms)

tc_summary %>%
  filter(is_cluster == "no") %>%
  arrange(desc(prevalence)) %>%
  select(topic, prevalence, coherence, is_cluster, top_terms)

tc_summary %>%
  filter(is_cluster == "yes") %>%
  arrange(desc(prevalence)) %>%
  select(topic, prevalence, coherence, is_cluster, top_terms)



```



## Compare models

```{r}

rm(list = ls())

load("data_derived/compare_models.RData")
```

```{r}

heatmap(lda_baseline_dist,
        main = "LDA baseline: model 1 to itself",
        Rowv = NA, Colv = NA)

heatmap(lda_12_dist,
        main = "LDA model 1 to model 2")

heatmap(lda_13_dist,
        main = "LDA model 1 to model 3")

heatmap(lda_23_dist,
        main = "LDA model 2 to model 3")

heatmap(lda_clust_dist,
        main = "LDA model 1 to clustering model")


```

# Compare evolution

```{r}
rm(list = ls())

load("data_derived/compare_transfer.RData")
```

```{r}

heatmap(comp_dists[[5]],
        Rowv = NA, Colv = NA,
        main = "Distance from 200 iterations to 1000 iterations")

ggplot(comp_topic_349) + 
  geom_line(aes(x = iterations, y = value, color = token)) +
  labs(title = "Change in P(token|topic = 349) during training")

```

